Data Analysis Project

### 2024-06-18 products/manuscript/Manuscript.qmd
commit changes

```{r}
#| label: fig-chidren
#| fig-cap: "Average Insurance Charges by Number of Children."
#| echo: FALSE
knitr::include_graphics(here("results","figures","children-bar.png"))
```

>>>>

```{r}
#| label: fig-children
#| fig-cap: "Average Insurance Charges by Number of Children."
#| echo: FALSE
knitr::include_graphics(here("results","figures","children-bar.png"))
```
